Decomposition-based Job-shop Scheduling with Constrained Clustering

### 2021-11-21 Artificial Intelligence and Machine Learning/PADL_conference/Paper_draft_v1.tex
some more progress in Section 4

Clustering algorithms are unsupervised learning methods whose goal is to partition a set of objects into (disjoint) subsets, called clusters, such that each cluster contains the most similar objects. 
The similarity of objects is determined by some measure, like Euclidian distance, using features of each object, such as features of operations extracted in the previous section. 
However, direct application of clustering algorithms, like K-Means \cite{Forgy1965ClusterAO}, in scheduling is limited since the partitioning cannot preserve the sequences of operations in a job. As a result, a clustering algorithm might place $O_{1,1}$ and $O_{1,3}$ in one cluster and $O_{1,2}$ in another. As a result, the sequence of sub-problems becomes inconsistent and no schedule can be found.

>>>>

Clustering algorithms are unsupervised learning methods whose goal is to partition a set of objects into (disjoint) clusters, such that each cluster gathers objects of high similarity. 
Such similarity is determined by some measure, e.g., Euclidean distance, based on features of each object, like the features of operations described in the previous section. 
However, the direct application of common clustering algorithms, such as K-Means~\cite{Forgy1965ClusterAO}, to scheduling problems is impractical since the partitioning does not take the sequence of operations in a job into account. For instance, a clustering algorithm may put $O_{1,1}$ and $O_{1,3}$ into the same and $O_{1,2}$ into another cluster. As a result, the sequence of time windows becomes inconsistent, and no compatible schedule exists.
